%
% File: abstract.tex
% Author: V?ctor Bre?a-Medina
% Description: Contains the text for thesis abstract
%
% UoB guidelines:
%
% Each copy must include an abstract or summary of the dissertation in not
% more than 300 words, on one side of A4, which should be single-spaced in a
% font size in the range 10 to 12. If the dissertation is in a language other
% than English, an abstract in that language and an abstract in English must
% be included.

\chapter*{Abstract}
\addstarredchapter{Abstract}
%\begin{vcenterpage}
{
\setstretch{}
\noindent\rule[3pt]{\textwidth}{1pt}
\vspace{.2cm}

\initial{I}n recent years virtualization has emerged as a core technology in the datacenters. In these datacenters, users tend to overdrive the resources of their applications, which leads to a waste of resources memory, low consolidation and low energy proportionality. Memory being the criticism of the resource, it would be advantageous to allocate to a machine the exact amount of memory it needs at a given moment. It is necessary so be able to wait for his request too to know at any time the size of his work package. Many techniques working set estimation already exist, based on software solutions that are intrusive and / or active, and which overload the virtual machine and / or the hypervisor. In this work we propose a technique of estimation which makes it possible to overcome the problems that software solutions pose. Indeed, our approach is based on a technology hardware the logging modification page (PML), which leaves it totally external to virtual machine (non-intrusive and non-active) and all the processes are done at dom0 level (no overloading of the virtual machine nor of the hypervisor).

\paragraph{Keywords : Virtualization, Working Set, PML, dom0.}

\vspace{.2cm}
\noindent\rule[3pt]{\textwidth}{1pt}
}
\clearpage